\documentclass{letter}
\usepackage{hyperref}

\begin{document}

\begin{letter}
{[Hiring Manager Name]\\
[Company Name]\\
[Company Address]}

Dear Hiring Manager,

I am writing to express my strong interest in the Software Engineer position at your organization. As a software engineer with expertise in automation, data pipelines, and machine learning systems, I am excited about contributing to your team's development efforts.

My background combines software engineering skills with practical experience in building scalable automation solutions. At ST Engineering, I developed C\#/Powershell automation suites integrating with Microsoft Office APIs, creating workflow solutions that reduced processing time from several months to one week. This demonstrates my ability to deliver practical software solutions that drive significant efficiency gains.

My experience at AMD provided valuable insight into software development for complex systems. I built Python-based data processing pipelines integrating PyANSYS simulations with machine learning workflows, developing open source automation tools that reduced computation time by 99.5\%. This experience taught me the importance of writing maintainable, scalable code for engineering applications.

My technical competencies include:
\begin{itemize}
  \item \textbf{Programming Languages:} Python, C\#, C, Golang, MATLAB, Mathematica
  \item \textbf{Automation Tools:} PowerShell, Microsoft Office API integration, workflow automation
  \item \textbf{Data Engineering:} NumPy, SciPy, pandas, PyTorch, data pipeline development
  \item \textbf{Development Tools:} Git, Linux systems, open source development
\end{itemize}

I am particularly drawn to this role because it offers the opportunity to apply my software engineering skills while continuing to solve complex technical challenges. I am committed to writing clean, maintainable code and would welcome the opportunity to discuss how my background can contribute to your team's success.

Thank you for your time and consideration. I look forward to hearing from you.

Sincerely,

Teo Yu Jie\\
8332 4860\\
yujie@protonmail.com\\
linkedin.com/in/yujieteo/\\
https://github.com/yujieteo?tab=repositories

\end{letter}

\end{document}